---
title: "madshapR-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{madshapR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# madshapR

Functions to support data cleaning, evaluation, and description, 
developed for integration with Maelstrom Research software tools. 'madshapR' 
provides functions primarily to evaluate and manipulate datasets and 
data dictionaries in preparation for data harmonization with the package 
'Rmonize' and to facilitate integration and transfer between RStudio servers 
and secure Opal environments. 'mapshapR' functions can be used independently
but are optimized in conjunction with ‘Rmonize’ functions for streamlined 
and coherent harmonization processing.

# Get started

## Install the package

```{r, eval=FALSE}
# Install madshapR and load the package:
install.packages('madshapR')
library(madshapR)

# If you need help with the package, please use:
madshapR_website()

# Example objects are available here
madshapR_examples

```
