---
title: "madshapR-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{madshapR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# madshapR

The madshapR package provides functions for efficient data cleaning, evaluation, 
and documentation across different datasets. It was developed to support work at 
Maelstrom Research and includes functions to evaluate and summarize datasets and 
their associated data dictionaries, identify potential issues in content and 
structure, and prepare datasets and metadata for further processing. The key 
outputs provided by the functions are formatted datasets, standardized metadata, 
and tabular and visual summary reports.

# Get started

## Install the package

```{r, eval=FALSE}
# To install madshapR:
install.packages('madshapR')

library(madshapR)
# If you need help with the package, please use:
madshapR_help()

# Downloadable templates are available here
madshapR_templates()

# Demo files are available here, along with an online demonstration process 
madshapR_DEMO

```
