---
title: "madshapR-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{madshapR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# madshapR

The goal of madshapR is to provide functions to support rigorous processes in 
data cleaning, evaluation, and documentation across datasets from different 
studies based on Maelstrom Research guidelines. The package includes the core 
functions to evaluate and format the main inputs that define the process, 
diagnose errors, and summarize and evaluate datasets and their associated 
data dictionaries. The main outputs are clean datasets and associated metadata, 
and tabular and visual summary reports.

# Get started

## Install the package

```{r, eval=FALSE}
# To update the R package in your R environment you may first need to remove 
# it, and use the exit command quit() to terminate the current R session.

# To install the R package:
install.packages('madshapR')
library(madshapR) 

#if you need help with the package, please use:
madshapR_help()

```
